Ion pairing controls rheological properties of ``processionary'' polyelectrolyte hydrogels

### 2016-07-08 PALSE/talk_Kyoto.tex
Flow curves + caterpillar, cite Srour MRC 2015

\begin{frame}{Physical polyelectrolytes hydrogel}
\let\mrad\relax
\newlength\mrad
\setlength{\mrad}{0.45em}
\tikzsetnextfilename{polyelectrolytes}%
\begin{tikzpicture}
\draw[every node/.style={circle,draw,font=\tiny, inner sep=0,minimum height=0.5em}] (0,0) --(30:\mrad) node[above right,ilmcolor]{-} (0,0)--(-30:\mrad) node[below right,ilmcolor]{-} (0,0)--++(-180:\mrad)\foreach \x [evaluate=\x as \r using 1/(rnd+0.1), evaluate=\x as \rr using 1/(rnd+0.1)] in {1,2,...,35}{--++(150:\mrad)node[above,ilmorange]{+} node[above=\r\mrad]{-}--++(-150:\mrad)node[below=0,ilmorange]{+} node[below=\rr\mrad]{-}};
\end{tikzpicture}

\begin{columns}
\column{0.5\textwidth}
\structure{Reversible gel}
\begin{itemize}
	\item in deionised, neutral water
	\item yield stress fuild
\end{itemize}
\structure{Solution} if
\begin{itemize}
	\item ionic strength, pH
	\item non ionic head
\end{itemize}
$\Rightarrow$ Head-to-body ionic bonds
\column{0.5\textwidth}
\end{columns}
\end{frame}

>>>>

\begin{frame}{Physical polyelectrolytes hydrogel}
	\tikzsetnextfilename{polyelectrolytes}%
\input{fig_presentation/polyelectrolytes.pgf}
\begin{columns}
\column{0.5\textwidth}
\structure{Reversible gel}
\begin{itemize}
	\item in deionised, neutral water
	\item yield stress fuild
\end{itemize}
\structure{Solution} if
\begin{itemize}
	\item ionic strength, pH
	\item non ionic head
\end{itemize}
$\Rightarrow$ Head-to-body ionic bonds

\column{0.5\textwidth}
\hfill Herschel-Buckley law\\
\hfill $\sigma =\sigma_c + A \dot{\gamma}^n$
\tikzsetnextfilename{flowcurves}%
\input{fig_presentation/flowcurves.pgf}
\end{columns}
\vspace{-\baselineskip}\textit{\scriptsize Srour et al. Macromol. Rapid Comm., 36, 55 (2015)}
\end{frame}
